Untrusted B2B Collaboration using the Blockchain

### 2018-07-23 paper/paper.tex
proof read, add more todos

	\keywords{Business Processes \and BPMN \and Choreographies \and Blockchain \and Ethereum \and Smart Contracts}
\end{abstract}
%
%
%
% TODO casing of headlines (capital)
\section{Introduction}

@@

Weber et al.~\cite{weber2016untrusted} realize Orchestrations on the Blockchain.

@@

When speaking about a Buisiness Process with multiple participants, there are generally two types of perspectives the Process Model can have: Orchestrations and Choreographies.
Orchestrations view the Process from a central perspective, and contain only one main pool which the process is focused around. 
They describe the internal process of an organization represented by the pool.
External communication partners can be included as pools aswell, however their internal processes are not modeled.
This gives the model a clear state and order in which it has to be executed.
The main pool inhibits the role of a mediator or manager, dictating and guiding the execution.

@@

One of the main ways our solution differs from the solution of Weber et al.~\cite{weber2016untrusted} is in the interpretation of orchestration and choreography.
Weber et al. implement choreographies by means of a central mediator/monitor contract.
Thus every step in the process is managed by this central contract.
The contract also holds an internal state of the process.
By our interpretation of the terms, this would not be a choreography but an orchestration.
Therefore we wanted to implement a solution, which models each pool seperately as their own entity, including having their own contracts.
Our goal is to decrease the amount trust needed between the communication partners.
By giving every pool their own set of contracts, we can make sure that every pool has control over the part of the process that is most relevant to them.

@@

%TODO add a step where other factory contracts are set
Each organization needs to perform some setup before they can take part in a process execution.
An access contract and a factory contract for a process need to be deployed it it has not been done yet.
Additionally, the user-to-role and and task-to-role mappings have to be updated, to allow verification of users during the process execution.
A diagram of this process can be seen in Figure \ref{fig:initialization}.

@@

Having achieved a traceable communication on the blockchain using contract function calls, we still want to access messages in off-chain applications, e.g., triggering process events in a process engine on message receive.
To this end, smart contracts need to implement events that are omitted to the blockchain whenever a receive function is executed.
Blockchain events can then be watched, and reacted upon, by off-chain components.

>>>>

	\keywords{Business Processes \and BPMN \and Choreographies \and Blockchain \and Ethereum \and Smart Contracts}
\end{abstract}
%
%
%
% TODO casing of headlines (capital)
\section{Introduction}
% TODO: rewrite introduction

@@

% TODO write more here
Weber et al.~\cite{weber2016untrusted} realize Orchestrations on the Blockchain.

@@

% TODO improve wording
When speaking about a Buisiness Process with multiple participants, there are generally two types of perspectives the Process Model can have: Orchestrations and Choreographies.
Orchestrations view the Process from a central perspective, and contain only one main pool which the process is focused around. 
They describe the internal process of an organization represented by the pool.
External communication partners can be included as pools aswell, however their internal processes are not modeled.
This gives the model a clear state and order in which it has to be executed.
The main pool inhibits the role of a mediator or manager, dictating and guiding the execution.

@@

One of the main ways our solution differs from the solution of Weber et al.~\cite{weber2016untrusted} is in the interpretation of orchestration and choreography.
Weber et al. implement choreographies by means of a central mediator/monitor contract.
Thus every step in the process is managed by this central contract.
The contract also holds an internal state of the process.
By our interpretation of the terms, this would not be a choreography but an orchestration.
Therefore we wanted to implement a solution, which models each pool seperately as their own entity, including having their own contracts.
Our goal is to decrease the amount of trust needed between the communication partners.
By giving every pool their own set of contracts, we can make sure that every pool has control over the part of the process that is most relevant to them.

% TODO write about public and private processes

@@

%TODO add a step where other factory contracts are set
Each organization needs to perform some setup before they can take part in a process execution.
An access contract and a factory contract for a process need to be deployed, if it has not been done yet.
Additionally, the user-to-role and and task-to-role mappings have to be updated, to allow verification of users during the process execution.
A diagram of this process can be seen in Figure \ref{fig:initialization}.

@@

Having achieved a traceable communication on the blockchain using contract function calls, we still want to access messages in off-chain applications, e.g., triggering process events in a process engine on message receive.
To this end, smart contracts need to implement events that are emitted to the blockchain whenever a receive function is executed.
Blockchain events can then be watched, and reacted upon, by off-chain components.
